
\documentclass[a4paper]{article} %
\usepackage{graphicx,amssymb} %

\textwidth=15cm \hoffset=-1.2cm %
\textheight=25cm \voffset=-2cm %

\pagestyle{empty} %

\date{} %

\def\keywords#1{\begin{center}{\bf Keywords}\\{#1}\end{center}} %

\def\titulo#1{\title{#1}} %
\def\autores#1{\author{#1}} %

% Please, do not change any of the above lines








\begin{document}

% Type down your paper title
\titulo{Sample \LaTeX\ abstract for ACA 2013 Proceedings}

% Authors
\autores{Gabriel Aguilera, Jos\'e Luis Gal\'an, Pedro Rodr\'{\i}guez \\ %
       University of M\'alaga (Spain) \\ \\ % Affiliation 1
       Gilles Picard \\ % If any other author with different Affilation
       University of Montreal (Canada) \\ \\ % Affiliation 2 (if needed)
       % New author \\
       % New affiliation \\
       % Add authors and affiliation as needed
       \tt{aca2013@ctima.uma.es} % Only one corresponding e-mail
       }%


\maketitle

\thispagestyle{empty}



% The abstract

\begin{abstract}
This is a sample abstract for submitting a talk proposal for any special session at ACA 2013. You
should send the tex file and a pdf version of your proposal.

Please, follow the specific submitting instructions for sending your proposal but do not forget to
send the tex and pdf versions.

You can check the list of accepted Special Session and any other information about the Conference
at {\tt http://aca2013.uma.es/}

Once your abstract is accepted, you can send to the Session chair(s) of the corresponding Special
Session an extended version (short paper up to 5 pages) in order to be included in the Proceedings
(with ISBN).

In case you want to send an extended version for Proceedings, you should follow the standard {\tt
section} and {\tt subsection} structure. The extended version should start with an introduction
section and Bibliography should be the last part. Please, remember that extended version should not
be longer than 5 compiled pages.

In case you do not want to send an extended version, only a one/two page(s) abstract will be
published in the Proceedings.

\end{abstract}

\keywords{Sample document, ACA 2013, Abstract submission, Paper submission} % Write down at least 3 Keywords






% \section{Introduction}






\end{document}
